---
title: "fars_vignette"
author: "Rudy Meza "
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEngine{knitr::knitr}
  %\VignetteIndexEntry{Title of your vignette}
  %\usepackage[UTF-8]{inputenc}
  
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The fars Package reads an example dataset from the  US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.


```{r, eval=F}
library(myfarspackage)
```

## Package Dependencies

The `fars` package imports packages - `readr`, `dplyr`, `tidyr`,`tidyverse`
It imports functions from packages - `maps`, `read_csv`, `points`.

## Export Functions

The `fars` package comprises of several functions -

- `fars_map_state`
- `fars_read`
- `fars_read_years`
- `fars_summarize_years`
- `make_filename`


## Using the Package

After importing the package, you can use the available functions -

**1. `make_filename` **

The purpose of this function is to add year of file to file_name_output


```{r, eval=F}
make_filename(2014)
```

**2. `fars_read_years` **

The purpose of this function is to filter list of dataframes and select month and year of dataframe

```{r, eval=F}
fars_read_years(c(2013, 2014)
```

**3. `fars_summarize_years` **

The purpose of this function is to filter and groupby month and state, then total up the accidents

```{r, eval=F}
 fars_summarize_years(2013)
```


**4. `fars_map_state` **

The purpose of this function is plot the coordinates of the state and show accidents.

```{r, eval=F}
 fars_summarize_years(1,2013)
```
